Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-28 Scripts/Initial_Analysis.Rmd
log transformed bubble plot

>>>>

##### Fig. 3. Bubble plot

```{r, buble_plot, eval = F, echo = F}

Buble_data <- Eez_d_hist %>% 
  filter(metric == "mean_yr") %>% 
  group_by(sau_fishing_entity,tresh) %>% 
  summarise(mean_yr = mean(value)) %>% 
  left_join(Eme_value_data,
            by = c("sau_fishing_entity","tresh")) %>% 
  filter(tresh == tresh_list[i],
         variable == "value") %>% 
  mutate(
    weight_toe = sum_value/mean_yr,
    sum_value_mi = sum_value/1000000000,
         logvalue = log10(sum_value)
         ) %>%   # Billion usd
  left_join(Matching_names,
            by = c("sau_fishing_entity","fishing_entity_id")) %>% 
  distinct(sau_fishing_entity,.keep_all = TRUE) %>% 
  filter(!is.na(un_geo_region)) %>% 
  ungroup() %>% 
  mutate(
    sau_fishing_entity = ifelse(sum_value_mi >= 1 & !sau_fishing_entity %in% c("Spain"), paste(sau_fishing_entity,"*",sep = ""),sau_fishing_entity)
  )

# Labels Data

Labels_data <- tibble(
  x = c(2020,2040,2070),
  y = c(0.3,0.3,9.1),
  label = c("Early emergence", "Late emergence","Fisheries over the 75 percentile")
)

# Plot the bubbles!

ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      # y = sum_value_mi,
      y = logvalue,
      size = n_taxa,
      colour = un_geo_region
    ),
    alpha = 0.7
  ) +
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(yintercept = 9, color = "grey90", size = 0.5)  +
  geom_label_repel(data = subset(Buble_data, sum_value_mi >= 1),
                   aes(
                     x = mean_yr,
                     # y = sum_value_mi,
                     y = logvalue,
                     label = sau_fishing_entity
                   ),
                   arrow = arrow(length = unit(0.009, "npc"),
                                 type = "closed",
                                 ends = "first"),
                   force = 3,
                   box.padding = 2,
                   fill = "NA"

  ) +
  geom_text(data = Labels_data,
    aes(
      x = x,
      y = y,
      label = label
    ),
    size = 3,
    color = "grey30"
  ) +
  # scale_fill_viridis(discrete = F)
  scale_color_viridis(name="Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     limits = c(2000,2080),
                     breaks = seq(2000,2080,10)
  ) +
  scale_y_continuous("Fishing revenue (log10)",
                     limits = c(3,12),
                     breaks = seq(3,12,3),
                     expand = c(0,0)
  ) +
  scale_size("Number of\nemerging taxa") +
  ggsave("./Figures/bubble_plot.png",
         width = 8,
         height = 8,
         units = "in"
  )
